---
title: "Can We Judge a Movie by its Poster?"
author: "Madeleine Ashby, Ayushi Ambhore, Sahil Patel"
date: "11/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Import necessary libraries / packages
library(readxl)
library(dplyr)
library(ggplot2)
library(tstools)

```

# Hypothesis
Using a supervised machine learning model taking into account features like dominant color, presence of faces, and amount of whitespace, we will be able to predict revenue for movies with 60% accuracy.

# Exploratory Data Analysis

## Data Collection
In order to explore our hypothesis, we needed to find a database of movies with information including the poster, gross revenue, etc. The data we are using was obtained from Kaggle [1] and it’s a list of IMDB top 100 movies in csv format. It contains the information that is relevant to our hypothesis and contains movies from 1920-2020.

## Data Cleaning
```{r}
# Load in data
movies <- read_excel("C:/Users/Maddie/OneDrive/Desktop/4YEAR/DS4002/Project3/ds4002-proj3/DATA/imdb_top_1000.xlsx")

# Drop unnecessary columns
movies <- movies[,c(1,2,3,6,7,16)]

# Drop rows with NA values
movies <- na.omit(movies)
movies <- subset(movies, movies$Released_Year!="PG")

```


```{r}
# IMDB Rating Count
ggplot(movies, aes(x=IMDB_Rating)) + geom_bar() + ggtitle("Number of Movies per IMDB Rating")
```
```{r}

ggplot(movies, aes(x=Released_Year, y=Gross)) + geom_point() + ggtitle("Revenue vs Time") + theme(axis.text.x=element_text(angle = 90, vjust = 0.5))



```

